Solar wind, F10.7, and geomagnetic activity relationship to the equatorial plasma mass density at geosynchronous orbit

### 2016-10-19 paper/paper.template.tex
Filling out AGU template

%\documentclass[11pt,twocolumn]{article}
%\usepackage{graphicx}
%\usepackage{fancyhdr}
%\usepackage{amssymb,amsmath}
%\usepackage[usenames,dvipsnames]{color}
%\usepackage[colorlinks,citecolor=RedViolet,urlcolor=blue]{hyperref}
%\usepackage{doi}
%\usepackage{setspace}
%\usepackage[paperwidth=8.5in, paperheight=11in,top=1in, bottom=1in, left=1in, r%ight=1in]{geometry}
%\usepackage[compact]{titlesec}
%\usepackage{abstract}
%\usepackage[position=t,singlelinecheck=off,justification=raggedleft]{subcaption}
%\usepackage[authoryear,square]{natbib}
%\usepackage{aas_macros}
%\usepackage{array}
%\pagestyle{fancy}
%\fancyhead[R]{Veibell \thepage}
%\fancyhead[L]{}

%\newcolumntype{L}{>{$}l<{$}} %To enable math mode in tables (for saying things like B_z)
%\newcolumntype{C}{>{$}c<{$}}
%\newcommand{\vinote}[1]{\textcolor{red}{\textbf{#1}}} %If you want \inote{#} instead of just \note #, for inline notes
%\def\vnote#1\par{\textcolor{red}{\textbf{#1}}\\} %Make note bold and red, re-add newline
%\newcommand{\req}{\ensuremath{\rho_{eq}}}
%\newcommand{\inote}[1]{\textcolor{blue}{\textbf{#1}}} %Inline notes in blue
%\def\note#1\par{\textcolor{blue}{\textbf{#1}}\\}

\documentclass[12pt]{article}
\bibliographystyle{./style/agufull}
\usepackage[square,comma,authoryear]{natbib}
\usepackage{aas_macros}
\usepackage{epsfig}
\usepackage{amsmath}
\usepackage{style/lineno}
\usepackage[hidelinks]{hyperref}
%\usepackage{url}

%\usepackage{booktabs}
\linenumbers*[1]
\usepackage{subfig}

\usepackage{setspace}  
\usepackage{fancyhdr}

\newcommand{\citeay}[1]{%
\citeauthor{#1}, \citeyear{#1}%
}

\pagestyle{fancy}
\fancyhead{}
\fancyfoot{}
\fancyhead[R]{X - \thepage}
\fancyhead[L]{VEIBELL: MASS DENSITY AT GEO}
\fancyfoot[L]{D R A F T}
\fancyfoot[C]{\today}
\fancyfoot[R]{D R A F T}
\renewcommand{\headrulewidth}{0.0pt}
\renewcommand{\footrulewidth}{0.0pt}
\oddsidemargin 0.0in
\evensidemargin 1.0in
\textwidth 6.5in
\headheight 0.1in
\topmargin -0.5in
\textheight 9.0in

\begin{document}
\title{Solar wind, F10.7, and geomagnetic activity relationship to the equatorial plasma mass density at geosynchronous orbit}
\author{V. Veibell, R.S. Weigel, and R.E. Denton}
\doublespacing
\maketitle

%\author{
%Victoir Veibell\footnote{vveibell@gmu.edu}
%\and
%R.S. Weigel\footnote{rweigel@gmu.edu}}

%\setlength{\parskip}{3ex}

%\titlespacing{\section}{0pc}{0.2pc}{-1pc}
%\titlespacing{\subsection}{0pc}{0.1pc}{-1pc}
%\titleformat*{\section}{\normalsize\bfseries}
%\titleformat*{\subsection}{\small\bfseries}

%\twocolumn[
%  \begin{@twocolumnfalse}
%\maketitle
%\hrule

% Key points
% Hourly averages are required to show a statistically significant mass density response during high geomagnetic activity
% The response of mass density for high geomagnetic activity intervals is strongest when F10.7 is elevated
% There is no solar wind variation signature associated with large mass density events

% Reviewers
% Takahashi
% O'Brien
% Denton
% Galager
% Singer

\begin{abstract}
We consider two types of events, identified by decreases in $D_{st}$ below a threshold value and increases in the equatorial mass density at geosynchronous altitudes, $\rho_{eq}$, above a threshold value using the \citet{Takahashi2010} dataset.  From the $D_{st}$ events and 1-day averages, we find that there is a statistically weak and small-amplitude difference between $\rho_{eq}$ on the day of the event and the days before and after.  When hourly averages are considered, a significant peak is found to occur six hours after event onset, and the primary factor that determines the post-onset peak amplitude in $\rho_{eq}$ is elevated $F10.7$.  In addition, for hourly averages, $\rho_{eq}$ following the onset of a $D_{st}$ event depends on the north-south component of the interplanetary magnetic field, $B_z$ after the time of onset, with higher average $B_{z}$ four hours after the event onset corresponding to larger $\rho_{eq}$ value 7-11 hours after onset.  From the $\rho_{eq}$ events, we find a weak dependence on $B_{z}$ after the onset of an event, with higher average $B_{z}$ four hours after the event onset corresponding to larger $\rho_{eq}$ values 24-36 hours after onset.
\end{abstract}
%\vspace{2em}
%\hrule
%\vspace{2em}
% \end{@twocolumnfalse}
%  ]

%\saythanks

@@

\section{Acknowledgements}

Work at Dartmouth College was supported by NSF grant AGS-1105790.

The mass density data used for this work can be obtained from \url{http://www.dartmouth.edu/~rdenton} and the gap-filled solar wind data is available at \url{http://virbo.org/ftp/users/kondrashov/}.

\newpage
%\footnotesize
%\bibliographystyle{plainnat}
%\bibliography{paper}

@@

\end{thebibliography}

>>>>

%% 11/23/2015
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% AGUJournalTemplate.tex: this template file is for articles formatted with LaTeX
%
% This file includes commands and instructions
% given in the order necessary to produce a final output that will
% satisfy AGU requirements. 
%
% You may copy this file and give it your
% article name, and enter your text.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PLEASE DO NOT USE YOUR OWN MACROS
% DO NOT USE \newcommand, \renewcommand, or \def, etc.
%
% FOR FIGURES, DO NOT USE \psfrag or \subfigure.
% DO NOT USE \psfrag or \subfigure commands.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% All questions should be e-mailed to latex@agu.org.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Step 1: Set the \documentclass
%
% There are two options for article format:
%
% 1) PLEASE USE THE DRAFT OPTION TO SUBMIT YOUR PAPERS.
% The draft option produces double spaced output.
% 
% 2) numberline will give you line numbers.

%% To submit your paper:
\documentclass[draft,linenumbers]{agujournal}
\draftfalse

%% For final version.
% \documentclass{agujournal}

% Now, type in the journal name: \journalname{<Journal Name>}

% ie, \journalname{Journal of Geophysical Research}
%% Choose from this list of Journals:
%
% JGR-Atmospheres
% JGR-Biogeosciences
% JGR-Earth Surface
% JGR-Oceans
% JGR-Planets
% JGR-Solid Earth
% JGR-Space Physics
% Global Biochemical Cycles
% Geophysical Research Letters
% Paleoceanography
% Radio Science
% Reviews of Geophysics
% Tectonics
% Space Weather
% Water Resource Research
% Geochemistry, Geophysics, Geosystems
% Journal of Advances in Modeling Earth Systems (JAMES)
% Earth's Future
% Earth and Space Science
%
%

\journalname{Space Weather}

\begin{document}

%% ------------------------------------------------------------------------ %%
%  Title
% 
% (A title should be specific, informative, and brief. Use
% abbreviations only if they are defined in the abstract. Titles that
% start with general keywords then specific terms are optimized in
% searches)
%
%% ------------------------------------------------------------------------ %%

% Example: \title{This is a test title}

\title{Solar wind, F10.7, and geomagnetic activity relationship to the equatorial plasma mass density at geosynchronous orbit}

%% ------------------------------------------------------------------------ %%
%
%  AUTHORS AND AFFILIATIONS
%
%% ------------------------------------------------------------------------ %%

% Authors are individuals who have significantly contributed to the
% research and preparation of the article. Group authors are allowed, if
% each author in the group is separately identified in an appendix.)

% List authors by first name or initial followed by last name and
% separated by commas. Use \affil{} to number affiliations, and
% \thanks{} for author notes.  
% Additional author notes should be indicated with \thanks{} (for
% example, for current addresses).

% Example: \authors{A. B. Author\affil{1}\thanks{Current address, Antartica}, B. C. Author\affil{2,3}, and D. E.
% Author\affil{3,4}\thanks{Also funded by Monsanto.}}

\authors{V. Veibell\affil{1}, R.S. Weigel\affil{1}, and R.E. Denton\affil{2}}

% \affiliation{1}{First Affiliation}
% \affiliation{2}{Second Affiliation}
% \affiliation{3}{Third Affiliation}
% \affiliation{4}{Fourth Affiliation}

\affiliation{1}{George Mason University}
\affiliation{2}{Dartmouth University}
%(repeat as many times as is necessary)

%% Corresponding Author:
% Corresponding author mailing address and e-mail address:

% (include name and email addresses of the corresponding author.  More
% than one corresponding author is allowed in this LaTeX file and for
% publication; but only one corresponding author is allowed in our
% editorial system.)

% Example: \correspondingauthor{First and Last Name}{email@address.edu}

%\correspondingauthor{=name=}{=email address=}

%% Keypoints, final entry on title page.

% Example: 
% \begin{keypoints}
% \item	List up to three key points (at least one is required)
% \item	Key Points summarize the main points and conclusions of the article
% \item	Each must be 100 characters or less with no special characters or punctuation 
% \end{keypoints}

%  List up to three key points (at least one is required)
%  Key Points summarize the main points and conclusions of the article
%  Each must be 100 characters or less with no special characters or punctuation

\begin{keypoints}
\item = enter point 1 here = 
\item = enter point 2 here = 
\item = enter point 3 here = 
\end{keypoints}

%% ------------------------------------------------------------------------ %%
%
%  ABSTRACT
%
% A good abstract will begin with a short description of the problem
% being addressed, briefly describe the new data or analyses, then
% briefly states the main conclusion(s) and how they are supported and
% uncertainties. 
%% ------------------------------------------------------------------------ %%

%% \begin{abstract} starts the second page

\begin{abstract}
We consider two types of events, identified by decreases in $D_{st}$ below a threshold value and increases in the equatorial mass density at geosynchronous altitudes, $\rho_{eq}$, above a threshold value using the \citet{Takahashi2010} dataset.  From the $D_{st}$ events and 1-day averages, we find that there is a statistically weak and small-amplitude difference between $\rho_{eq}$ on the day of the event and the days before and after.  When hourly averages are considered, a significant peak is found to occur six hours after event onset, and the primary factor that determines the post-onset peak amplitude in $\rho_{eq}$ is elevated $F10.7$.  In addition, for hourly averages, $\rho_{eq}$ following the onset of a $D_{st}$ event depends on the north-south component of the interplanetary magnetic field, $B_z$ after the time of onset, with higher average $B_{z}$ four hours after the event onset corresponding to larger $\rho_{eq}$ value 7-11 hours after onset.  From the $\rho_{eq}$ events, we find a weak dependence on $B_{z}$ after the onset of an event, with higher average $B_{z}$ four hours after the event onset corresponding to larger $\rho_{eq}$ values 24-36 hours after onset.
\end{abstract}

@@

\acknowledgments
Work at Dartmouth College was supported by NSF grant AGS-1105790.

The mass density data used for this work can be obtained from http://www.dartmouth.edu/~rdenton and the gap-filled solar wind data is available at http://virbo.org/ftp/users/kondrashov/.

%% ------------------------------------------------------------------------ %%
%% Citations

% Please use ONLY \citet and \citep for reference citations.
% DO NOT use other cite commands (e.g., \cite, \citeyear, \nocite, \citealp, etc.).

%% Example \citet and \citep:
%  ...as shown by \citet{Boug10}, \citet{Buiz07}, \citet{Fra10},
%  \citet{Ghel00}, and \citet{Leit74}.

%  ...as shown by \citep{Boug10}, \citep{Buiz07}, \citep{Fra10},
%  \citep{Ghel00, Leit74}.

%  ...has been shown \citep [e.g.,][]{Boug10,Buiz07,Fra10}.

%%  REFERENCE LIST AND TEXT CITATIONS
%
% Either type in your references using
%
% \begin{thebibliography}{}
% \bibitem[{\textit{Kobayashi et~al.}}(2003)]{R2013} Kobayashi, T.,
% Tran, A.~H., Nishijo, H., Ono, T., and Matsumoto, G.  (2003).
% Contribution of hippocampal place cell activity to learning and
% formation of goal-directed navigation in rats. \textit{Neuroscience}
% 117, 1025--1035.
%
% \bibitem{}
% Text
% \end{thebibliography}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Or, to use BibTeX:
%
% Follow these steps
%
% 1. Type in \bibliography{<name of your .bib file>} 
%    Run LaTeX on your LaTeX file.
%
% 2. Run BiBTeX on your LaTeX file.
%
% 3. Open the new .bbl file containing the reference list and
%   copy all the contents into your LaTeX file here.
%
% 4. Run LaTeX on your new file which will produce the citations.
%
% AGU does not want a .bib or a .bbl file. Please copy in the contents of your .bbl file here.

%% After you run BibTeX, Copy in the contents of the .bbl file here:

@@

\end{thebibliography}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Track Changes:
% To add words, \added{<word added>}
% To delete words, \deleted{<word deleted>}
% To replace words, \replace{<word to be replaced>}{<replacement word>}
% To explain why change was made: \explain{<explanation>} This will put
% a comment into the right margin.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% At the end of the document, use \listofchanges, which will list the
% changes and the page and line number where the change was made.

% When final version, \listofchanges will not produce anything,
% \added{<word or words>} word will be printed, \deleted{<word or words} will take away the word,
% \replaced{<delete this word>}{<replace with this word>} will print only the replacement word.
%  In the final version, \explain will not print anything.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%
%\listofchanges
%%%
